RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-21 paper/paper7/paper7.tex
feedback from Achim and Kai

Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
which is available for contribution at \url{http://purl.org/net/rdf-validation}.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
Bosch and Eckert \cite{BoschEckert2014-2} \tb{why do we use spin?}use SPIN as basis to define a
validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.

@@

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-, three-, or four-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
Aggregated data is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
%allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
%Although, in most cases aggregated data is still published in form of PDFs, 
%it is more and more common to publish aggregated data as CSV files,
Aggregated data is more and more published as CSV files,
allowing to perform first data calculations.
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

@@

We developed a system to classify RDF constraints and RDF constraint types.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
%\emph{data model specific constraint types} (e.g. \emph{data model consistency})
The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses two disjoint \textbf{\emph{sets of constraint types}}:
\begin{enumerate}
	\item $\mathcal{CT}_{C}$: \emph{Content-Driven Constraint Types}
	\item $\mathcal{CT}_{T}$: \emph{Technology-Driven Constraint Types}
\end{enumerate}

@@

We determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
	\item $\mathcal{SL}_{1}$: set of constraints with severity level \emph{warning}
	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be
whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
Although, we provide default severity levels for each constraint, users should be able to specify constraints' severity levels according to their individual needs, i.e., use case specific severity levels.

@@

For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.  
Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.

>>>>

Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
which is available for contribution at \url{http://purl.org/net/rdf-validation}.
The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
Bosch and Eckert \cite{BoschEckert2014-2} \tb{why do we use spin?not the best for constraint language, but for validating / akzeptierte beste form constraints zu definieren}use SPIN as basis to define a
validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.

@@

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-, three-, or four-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e. multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
Aggregated data is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
%allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
%Although, in most cases aggregated data is still published in form of PDFs, 
%it is more and more common to publish aggregated data as CSV files,
Aggregated data is more and more published as CSV files,
allowing to perform first data calculations.
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format.\tb{tabular data} 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

@@

We developed a system to classify RDF constraints and RDF constraint types.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
%\emph{data model specific constraint types} (e.g. \emph{data model consistency})
The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses two disjoint \textbf{\emph{sets of constraint types}}:
\begin{enumerate}
	\item $\mathcal{CT}_{C}$: \emph{Content-Driven Constraint Types}\tb{complex constraints / zahlen interpretierbar / in einem bestimten vokabulare werden viele basic constraints verletzt / daten haben bessere qualität vokabular / wichtigkeit constraint languages, dass complexe constraints beschrieben}
	\item $\mathcal{CT}_{T}$: \emph{Technology-Driven Constraint Types}\tb{basic constraints / welche constraints können automatisch abgeleitet werden / bestimmte constraints werden in den vokabularen definiert bzw sehr leicht zu implementieren wäre / studie ohne daten macht keinen sinn --> cardinality restriction / alle constraints die mit rdf + rdfs + owl definiert werden können / vokabukare werden heutzutage mit rdf / rdfs / owl beschrieben / constraints die typischerweise hinterlegt werden / constraints die amn als vokabular}
\end{enumerate}

\tb{große datenbestände untersuchen um ein besseres verständnis zu bekommen / liste von constraints / jedes einzelne constraint für jeded einzelne vokabular severity level / warum severity was bringt das}

@@

\emph{SBE} experts \tb{todo / wieviele constraints welche klasse} determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
\begin{itemize}
	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
	\item $\mathcal{SL}_{1}$: set of constraints with severity level \emph{warning}
	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
\end{itemize}
Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be
whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
Although, we provide default severity levels for each constraint, users should be able to specify constraints' severity levels according to their individual needs, i.e., use case specific severity levels.

@@

For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.  
Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.\tb{bezug nehmen auf severity levels / technology-driven werden oft eingehalten? / }
